---
title: "**Decision analysis of agro-climate service scaling** <br /> A case study in Dien Bien District, Vietnam"
author: Thi Thu Giang Luu^a,@^, Cory Whitney^a,b^ and Eike Luedeling^a^ <br /><small>^a^INRES-Horticultural Sciences, University of Bonn, Auf dem Huegel 6, 53121 Bonn, Germany <br /><small/>^b^Center of Development Research (ZEF), University of Bonn, Genscherallee 3, 53113 Bonn, Germany <br /><small/>^@^Corresponding author's email:luuthithugiang@gmail.com
bibliography: 
  - bib/packages.bib
output: 
  html_document:
    toc: true
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cowplot)
library(decisionSupport)
library(ggplot2)
library(knitr)
library(rmarkdown)
options(knitr.table.format = "html")
```

```{r, warning=FALSE, include = FALSE}
#Automatically write R package citation entries to a .bib file
knitr::write_bib(c(.packages(), 
                   'cowplot',
                   'decisionSupport', 
                   'ggplot2',
                   'knitr',
                   'rmarkdown'), 'bib/packages.bib')
```

This document describes the model simulation used for forecasting the potential outcomes of four different Agro-climate services (ACS) interventions in Vietnam. The model is programmed with the `decisionSupport` package [@R-decisionSupport]. The full model is available in the [ACS-Decision-Analysis repository](https://github.com/ThiThuGiangLuu/ACS-Decision-Analysis). 
# Model development process

The model described in this document was programmed in the R programming language [@R-base] using the `decisionSupport` library [@R-decisionSupport] among others. The full model that is described here can be found in the [ACS-Decision-Analysis repository](https://github.com/ThiThuGiangLuu/ACS-Decision-Analysis). The document was generated with the Rmarkdown and knitr libraries [@R-rmarkdown; @R-knitr].

## Input table 

The input table `acis_inputs_EN.csv` contains the the variables used in the model. The table includes the variable names, variable distribution, variable upper and lower bound estimates (90% confidence interval), variable descriptions and variable labels. Download the table from the [ACS-Decision-Analysis repository](https://github.com/ThiThuGiangLuu/ACS-Decision-Analysis). 

## Implement model in R

To illustrate important parts of the model line by line we create a `make_variables` function with the `decisionSupport` `estimate_read_csv` to produce a single draw of the variable distributions defined in the `acis_inputs_EN.csv` input table. 

```{r, warning=FALSE}
make_variables <- function(est, n = 1)
  {
  x <- random(rho = est,n = n)
  for(i in colnames(x))
    assign(i, as.numeric(x[1, i]),envir = .GlobalEnv)
  }
  
  make_variables(estimate_read_csv("acis_inputs_EN.csv"))
  
```

The code described below is wrapped in a function called `acis_costbenefit` in the [ACS decision analysis.R file](https://github.com/ThiThuGiangLuu/ACS-Decision-Analysis/blob/master/ACS%20decision%20analysis.R). The function is used to calculate the Net Present Values (NPV) of the investment decision in ACS. 

## Four ACS Interventions 

The four Agro-climatic Services (ACS) interventions considered in the model include:

<<<<<<< HEAD
```{r}
# This benefit is similar to all interventions 
# Drought risk for each year
# drought_risk_i1234<-chance_event(chance_drought_i1234,value_if = 1, n=n_years)
    
# Drought area for each year 
     rice_drought_i1234<-rep(0,n_years)
     rice_drought_i1234[1:5]<-rice_area_drought_i1234*drought_risk_i1234
=======
- Intervention 1: Weather station-SMS-gender
- Intervention 2: SMS-gender
- Intervention 3: SMS-loudspeaker
- Intervention 4: Paper-loudspeaker
>>>>>>> 65fd36684c6924b39017a7eec5bb6ec507652d0c
    
The risks, costs and benefits of the four internetions include: 

- i1: risk/cost/benefit variable incurred for intervention1
- i2: risk/cost/benefit variable incurred for intervention2
- i3: risk/cost/benefit variable incurred for intervention3
- i4: risk/cost/benefit variable incurred for intervention4
- i12: risk/cost/benefit variable incurred for intervention1 and intervention 2
- i234: risk/cost/benefit for intervention2, intervention3 and intervention 4
- i34: risk/cost/benefit for intervention3 and intervention 4
- i1234: risk/cost/benefit for all intervention1, intervention2, intervention 3 and intervention 4

### 1. Calculating chance event of risks and uncertainties

We used the `chance_event()` function to simulate the risks of having extreme weather events, chances of having inaccurate forecasts and the chances that cause additional agricultural input application due to weather events. This function will simulate the chance if an event may occur or not. As a result, the values of dependent variables may vary depending on the occurrence of the events. The output of the simulation can be single or series of values. For example we calculated the drought risk for each year in intervention1, intervention2, intervention 3 and intervention 4 with the `chance_event` function, using `chance_drought_i1234` and `n_years` from the input table.

```{r chance_event}
drought_risk_i1234 <- chance_event(chance_drought_i1234, 
                                   value_if = 1, 
                                   n = n_years)

drought_risk_i1234
```

We used the `vv()` function to introduce variation into time series variables. Inputs to run this function include the mean of the variable to be varied `var_mean`, desired coefficient of variation (in percent) `var_CV` and number of values to be produced `n`. For example when calculating the costs of buying weather forecasts from provincial meteorological station for for each year in intervention1, intervention2, intervention 3 and intervention 4: 

```{r}
    cost_forecast_province <- rep(0, n_years)
    cost_forecast_province[1:5] <- vv(cost_weekly_forecasts_i1234 +
                                    cost_seasonal_forecasts_i1234, 
                                    var_CV, 
                                    n_years)/exchange_rate
    
    cost_forecast_province
```

We considered economic benefits such as potential benefits for rice plantation from drought advice at the start of the season. For example we use the `rice_area_drought_i1234` from the input table and `drought_risk_i1234` calculated above to create a drought area we called `rice_area_drought_i1234` for each year in intervention1, intervention2, intervention 3 and intervention 4. 

```{r}
     rice_drought_i1234 <- rep(0, n_years)
     rice_drought_i1234[1:5] <- rice_area_drought_i1234*drought_risk_i1234
```

We used the input table and the model to run a Monte Carlo Simulation with the `decisionSupport` function in the `decisionSupport` package [@R-decisionSupport]. We define the number of model runs as of 10,000 models. We specify the `outputPath` to store decision outcome in specified folder `MCResults`.

```{r eval=FALSE}
  decisionSupport::decisionSupport(
  "acis_inputs_EN.csv",
  outputPath = paste("MCResults", sep = ""),
  welfareFunction = acis_costbenefit,
  numberOfModelRuns = 1e4, #run 10,000 times
  functionSyntax = "plainNames")
  
```

## Outcome distribution visualization

We extracted Net Present Values (NPV) and Benefit Cost Ratios (BCRs) from the file `MCResults\mcSimulationResults.csv` generated by the `decisionSupport` function [@R-decisionSupport]. We then visualize the probability distribution of NPVs and BCRs using `ggplot2` package [@R-ggplot2]. We combine the 2 graphs into a single graphs using `cowplot` package [@R-cowplot].  

## Acknowledgements

We acknowledge the valuable support from CARE in Vietnam and the Centre of Community Development (CCD). We thank the Schlumberger Foundation for providing a scholarship for the main author. We value the participation and support from expert team through out this study.  

## References


